### 2021-05-18 Paper.tex
modified

\subsection{Viscoplastic mantle convection}\label{sec:visco_mantle}
This benchmark is performed as described in \citet{Tosi2015} for Cases 1-5a. Table \ref{tab:visco_mantle}.WORK IN PROGRESS.

\renewcommand{\arraystretch}{1.5}
{\rowcolors{3}{white!100!}{gray!25!}
\begin{table}[H]
  \caption{Results of the viscoplastic mantle convection benchmark for Cases 1-4 compared with results obtained with ELEFANT and YACC (from \citealp{Tosi2015}).}
  \centering
  \resizebox{\textwidth}{!}{
\begin{tabular}{|c|ccc|ccc|ccc|ccc|}
  \toprule
    & \multicolumn{3}{c|}{\textbf{Case 1}} & \multicolumn{3}{c|}{\textbf{Case 2}} & \multicolumn{3}{c|}{\textbf{Case 3}} &
    \multicolumn{3}{c|}{\textbf{Case 4}} \\
   & FALCON & ELEFANT& YACC & FALCON& ELEFANT& YACC & FALCON & ELEFANT & YACC & FALCON & ELEFANT & YACC \\
  \midrule
   $\left\langle T \right\rangle$ & 0.7759 & 0.7758 & 0.7767 & & 0.6036 & 0.6058 & 0.7275 & 0.7275 & 0.7286 & & 0.5277 & 0.5289\\
    Nu$^{top}$ & 3.4280 & 3.4214 & 3.4298 & & 8.5115 & 8.5278 & 3.0368 & 3.0347 & 3.0374 && 6.5912 & 6.5572 \\
    Nu$^{bottom}$ & 3.3168 & 3.313 & 3.3143 & & 8.4465 & 8.3990 & 3.0086 & 2.9908 & 2.9628 && 6.5834 & 6.5243 \\
    $v_{\textrm{rms}}$ & 249.901 & 249.134 & 251.7997 & & 140.7087 & 142.2020 & 100.2776 & 100.1208 & 100.9467 && 79.1105 & 79.6202 \\
    $v_{\textrm{rms}}^{top}$ & 1.8907 & 1.8642 & 1.8298 & & 104.1228 & 105.1767 & 2.0832 & 2.0652 & 2.0374 && 74.7596 & 75.8414 \\
    $u_{max}^{top}$ & 2.6340 & 2.6119 & 2.5516 & & 121.766 & 122.3238 & 2.9086 & 2.9019 & 2.8458 && 88.9146 & 89.2940 \\
    $\eta_{min}$ & - & - & - & & $2.0600\times10^{-5}$ & $1.9853\times10^{-5}$ & $4.8129\times10^{-5}$ & $4.8080\times10^{-5}$ & $4.7907\times10^{-5}$ &
    & $1.9860\times10^{-4}$ & $1.9174\times10^{-4}$ \\
    $\eta_{max}$ & - & - & - & & 1.85 & 1.6095 & 0.9360 & 0.9023 & 1 && 1.52 & 1.6773 \\
    $\left\langle W \right\rangle$ & 2.4299 & 2.4316 & 2.4583 & & 7.5665 & 7.6222 & 2.0387 & 2.0384 & 2.0400 && 5.6216 & 5.6512 \\
    $\left\langle \Phi \right\rangle/Ra$ & 2.4311 & 2.4276 & 2.4333 & & 7.5585 & 7.6194 & 2.0386 & 2.0370 & 2.0335 && 5.6182 & 5.6463 \\
    $\delta$ & 0.05\% & 0.16\% & 1.02\% & & 0.11\% & 0.04\% & $<$0.01\% & 0.07\% & 0.32\% && 0.06\% & 0.09\% \\
  \bottomrule
  \end{tabular}}
  \label{tab:visco_mantle}
  \end{table}

>>>>

\subsection{Viscoplastic mantle convection}\label{sec:visco_mantle}
This benchmark is performed as Cases 1-5a described in \citet{Tosi2015}. Table \ref{tab:tosi_setup}. Table \ref{tab:visco_mantle}.WORK IN PROGRESS.

%\renewcommand{\arraystretch}{1.5}
%{\rowcolors{3}{white!100!}{gray!25!}
%\begin{table}[H]
%  \caption{Results of the viscoplastic mantle convection benchmark for Cases 1-4 compared with results obtained with ELEFANT and YACC (from \citealp{Tosi2015}).}
%  \centering
%  \resizebox{\textwidth}{!}{
%\begin{tabular}{|c|ccc|ccc|ccc|ccc|}
%  \toprule
%    & \multicolumn{3}{c|}{\textbf{Case 1}} & \multicolumn{3}{c|}{\textbf{Case 2}} & \multicolumn{3}{c|}{\textbf{Case 3}} &
%    \multicolumn{3}{c|}{\textbf{Case 4}} \\
%   & FALCON & ELEFANT& YACC & FALCON& ELEFANT& YACC & FALCON & ELEFANT & YACC & FALCON & ELEFANT & YACC \\
%  \midrule
%   $\left\langle T \right\rangle$ & 0.7759 & 0.7758 & 0.7767 & 0.6043 & 0.6036 & 0.6058 & 0.7275 & 0.7275 & 0.7286 & & 0.5277 & 0.5289\\
%    Nu$^{top}$ & 3.4280 & 3.4214 & 3.4298 & 8.5242 & 8.5115 & 8.5278 & 3.0368 & 3.0347 & 3.0374 && 6.5912 & 6.5572 \\
%    Nu$^{bottom}$ & 3.3168 & 3.313 & 3.3143 & 8.4599 & 8.4465 & 8.3990 & 3.0086 & 2.9908 & 2.9628 && 6.5834 & 6.5243 \\
%    $v_{\textrm{rms}}$ & 249.901 & 249.134 & 251.7997 & 141.2451 & 140.7087 & 142.2020 & 100.2776 & 100.1208 & 100.9467 && 79.1105 & 79.6202 \\
%    $v_{\textrm{rms}}^{top}$ & 1.8907 & 1.8642 & 1.8298 & 104.7928 & 104.1228 & 105.1767 & 2.0832 & 2.0652 & 2.0374 && 74.7596 & 75.8414 \\
%    $u_{max}^{top}$ & 2.6340 & 2.6119 & 2.5516 & 121.9212& 121.766 & 122.3238 & 2.9086 & 2.9019 & 2.8458 && 88.9146 & 89.2940 \\
%    $\eta_{min}$ & - & - & - & $2.0303\times10^{-5}$ & $2.0600\times10^{-5}$ & $1.9853\times10^{-5}$ & $4.8129\times10^{-5}$ & $4.8080\times10^{-5}$ & $4.7907\times10^{-5}$ &
%    & $1.9860\times10^{-4}$ & $1.9174\times10^{-4}$ \\
%    $\eta_{max}$ & - & - & - & 1.3325 & 1.85 & 1.6095 & 0.9360 & 0.9023 & 1 && 1.52 & 1.6773 \\
%    $\left\langle W \right\rangle$ & 2.4299 & 2.4316 & 2.4583 & 7.5648 & 7.5665 & 7.6222 & 2.0387 & 2.0384 & 2.0400 && 5.6216 & 5.6512 \\
%    $\left\langle \Phi \right\rangle/Ra$ & 2.4311 & 2.4276 & 2.4333 & 7.5661 & 7.5585 & 7.6194 & 2.0386 & 2.0370 & 2.0335 && 5.6182 & 5.6463 \\
%    $\delta$ & 0.05\% & 0.16\% & 1.02\% & 0.02\% & 0.11\% & 0.04\% & $<$0.01\% & 0.07\% & 0.32\% && 0.06\% & 0.09\% \\
%  \bottomrule
%  \end{tabular}}
%  \label{tab:visco_mantle}
%  \end{table}
%\renewcommand{\arraystretch}{1.5}
%{\rowcolors{2}{white!100!}{gray!25!}
\begin{table}[H]
  \caption{Benchmark cases and corresponding parameters.}
  \centering
  \small
\begin{tabular}{|>{\centering}m{0.08\textwidth}|>{\centering}m{0.05\textwidth}>{\centering}m{0.05\textwidth}>{\centering}m{0.05\textwidth}
  >{\centering}m{0.05\textwidth} >{\centering}m{0.05\textwidth} |>{\centering\arraybackslash}m{0.2\textwidth}|}
  \toprule
    Case & $Ra$ & $\Delta\eta_T$ & $\Delta\eta_y$ & $\eta^*$ & $\sigma_Y$ & Convective regime \\
  \midrule
  \rowcolor{gray!25!}
    1 & $10^2$ & $10^5$ & 1 & - & - & Stagnant lid \\
    2 & $10^2$ & $10^5$ & 1 & $10^{-3}$ & 1 & Mobile lid  \\
    \rowcolor{gray!25!}
    3 & $10^2$ & $10^5$ & 10 & - & - & Stagnant lid  \\
    4 & $10^2$ & $10^5$ & 10 & $10^{-3}$ & 1 & Mobile lid \\
    \rowcolor{gray!25!}
    5 & $10^2$ & $10^5$ & 10 & $10^{-3}$ & 4 & Periodic \\
  \bottomrule
  \end{tabular}
  \label{tab:tosi_setup}
  \end{table}

\renewcommand{\arraystretch}{1.5}
%{\rowcolors{3}{gray!25!}{white!100!}
\begin{table}[H]
  \caption{Results of the viscoplastic mantle convection benchmark for different grid resolutions in Cases 1-4 compared with results obtained with ELEFANT
  and YACC ($100\times100$ elements, from \citealp{Tosi2015}) and in Stone 28 ($32\times32$ elements, from
  \url{https://github.com/cedrict/fieldstone/tree/master/python_codes/fieldstone_28}).}
  \centering
  \resizebox{\textwidth}{!}{
\begin{tabular}{|cc|ccccccccccc|}
  \toprule
  \multicolumn{13}{|c|}{\textbf{Case 1}} \\
  \midrule
  Code & Resolution & $\left\langle T \right\rangle$ & Nu$^{top}$ & Nu$^{bottom}$ & $v_{\textrm{rms}}$ & $v_{\textrm{rms}}^{top}$& $u_{max}^{top}$& $\eta_{min}$
  & $\eta_{max}$ & $\left\langle W \right\rangle$ & $\left\langle \Phi \right\rangle/Ra$ & $\delta$ \\
  \hline
  \rowcolor{gray!25!}
    YACC & $100\times100$ & 0.7767 & 3.4298 & 3.3143 & 251.7997 & 1.8298 & 2.5516 & - & - & 2.4583 & 2.4333 & 1.02\% \\
    ELEFANT & $100\times100$ & 0.7758 & 3.4214 & 3.313 & 249.134 & 1.8642 & 2.6119 & - & - & 2.4316 & 2.4276 & 0.16\% \\
    \rowcolor{gray!25!}
    Stone 28 & $32\times32$ & 0.7737 & 3.3987 & - & 243.872 & - & - & - & - & - & - & - \\
%    FALCON & $32\times32$ & 0.7750 & 3.4381 & 2.7363 & 248.3337 & 2.0022 & 2.7813 & - & - & 2.4745 & 2.4864 & 0.48\% \\
%    \rowcolor{gray!25!}
    FALCON & $100\times100$ & 0.7759 & 3.4280 & 3.3168 & 249.901 & 1.8907 & 2.6340 & - & - & 2.4299 & 2.4311 & 0.05\% \\
    \midrule
    \multicolumn{13}{|c|}{\textbf{Case 2}} \\
    \midrule
    Code & Resolution & $\left\langle T \right\rangle$ & Nu$^{top}$ & Nu$^{bottom}$ & $v_{\textrm{rms}}$ & $v_{\textrm{rms}}^{top}$& $u_{max}^{top}$& $\eta_{min}$
    & $\eta_{max}$ & $\left\langle W \right\rangle$ & $\left\langle \Phi \right\rangle/Ra$ & $\delta$ \\
    \hline
    \rowcolor{gray!25!}
     YACC & $100\times100$ & 0.6058 & 8.5278 & 8.3990 & 142.2020 & 105.1767 & 122.3238 & $1.9853\times10^{-5}$ & 1.6095 & 7.6222 & 7.6194 & 0.04\% \\
     ELEFANT & $100\times100$ & 0.6034 & 8.5115 & 8.4465 & 140.8067 & 104.1228 & 121.766 & $2.0600\times10^{-5}$ & 1.85 & 7.5665 & 7.5585 & 0.11\% \\
     \rowcolor{gray!25!}
     Stone 28 & $32\times32$ & 0.6052 & 8.1715 & - & 141.518 & - & - & - & - & - & - & - \\
%     FALCON & $32\times32$ & 0.6454 & 8.1422 & 7.4020 & 156.6908 & 95.7226 & 116.9302 & $2.2572\times10^{-5}$ & 0.7194 & 7.4289 & 7.4452 & 0.22\% \\
%     \rowcolor{gray!25!}
     FALCON & $100\times100$ & 0.6044 & 8.5266 & 8.4590 & 141.3684 & 104.8867 & 122.0470 & $2.0333\times10^{-5}$ & 1.2914 & 7.5707 & 7.5718 & 0.01\% \\
     \midrule
     \multicolumn{13}{|c|}{\textbf{Case 3}} \\
     \midrule
     Code & Resolution & $\left\langle T \right\rangle$ & Nu$^{top}$ & Nu$^{bottom}$ & $v_{\textrm{rms}}$ & $v_{\textrm{rms}}^{top}$& $u_{max}^{top}$& $\eta_{min}$
     & $\eta_{max}$ & $\left\langle W \right\rangle$ & $\left\langle \Phi \right\rangle/Ra$ & $\delta$ \\
     \hline
     \rowcolor{gray!25!} 
     YACC & $100\times100$ & 0.7286 & 3.0374 & 2.9628 & 100.9467 & 2.0374 & 2.8458 & $4.7907\times10^{-5}$ & 1 & 2.0400 & 2.0335 & 0.32\% \\
      ELEFANT & $100\times100$ & 0.7275 & 3.0347 & 2.9908 & 100.1208 & 2.0652 & 2.9019 & $4.8080\times10^{-5}$ & 0.9023 & 2.0384 & 2.037 & 0.07\% \\
      \rowcolor{gray!25!}
      Stone 28 & $32\times32$ & 0.7277 & 3.0347 & - & 100.018 & - & - & - & - & - & - & - \\
%      FALCON & $32\times32$ & 0.7281 & 3.0618 & 2.8132 & 101.0092 & 2.1630 & 3.0178 & $4.8500\times10^{-5}$ & 0.7845 & 2.0699 & 2.0695 & 0.02\% \\
%      \rowcolor{gray!25!}
      FALCON & $100\times100$ & 0.7275 & 3.0368 & 3.0086 & 100.2776 & 2.0832 & 2.9086 & $4.8129\times10^{-5}$ & 0.9360 & 2.0387 & 2.0386 & $<$0.01\% \\
      \midrule
      \multicolumn{13}{|c|}{\textbf{Case 4}} \\
      \midrule
      Code & Resolution & $\left\langle T \right\rangle$ & Nu$^{top}$ & Nu$^{bottom}$ & $v_{\textrm{rms}}$ & $v_{\textrm{rms}}^{top}$& $u_{max}^{top}$& $\eta_{min}$
      & $\eta_{max}$ & $\left\langle W \right\rangle$ & $\left\langle \Phi \right\rangle/Ra$ & $\delta$ \\
      \hline
      \rowcolor{gray!25!} 
      YACC & $100\times100$ & 0.5289 & 6.5572 & 6.5243 & 79.6202 & 75.4814 & 89.2940 & $1.9174\times10^{-4}$ & 1.6773 & 5.6512 & 5.6463 & 0.09\% \\
       ELEFANT & $100\times100$ & 0.5277 & 6.5912 & 6.5834 & 79.1105 & 74.7596 & 88.9146 & $1.9860\times10^{-4}$ & 1.5200 & 5.6216 & 5.6182 & 0.06\% \\
       \rowcolor{gray!25!}
       Stone 28 & $32\times32$ & 0.5286 & 6.4036 & - & 79.4746 & - & - & - & - & - & - & - \\
%       FALCON & $32\times32$ & 0.5334 & 6.4679 & 6.3435 & 80.6153 & 76.0511 & 90.2058 & $2.0393\times10^{-4}$ & 0.6453 & 5.6676 & 5.6698 & 0.04\% \\
%       \rowcolor{gray!25!}
       FALCON & $100\times100$ & 0.5279 & 6.5897 & 6.5830 & 79.1220 & 75.0715 & 88.8484 & $1.9693\times10^{-4}$ & 1.4133 & 5.6127 & 5.6113 & 0.03\% \\
  \bottomrule
  \end{tabular}}
  \label{tab:visco_mantle}
  \end{table}
